---
title: "final-paper"
author: "Anne Lee Steele"
date: "09/12/2019"
output: html_document
---
# Final Project
## Load Packages
```{r}
library(ergm) 
library(sna) 
library(coda)
library(latticeExtra)
library(igraph)
library(sna)
library(dplyr)
library(netdiffuseR)
library(igraph)
library(cluster)
library(NetCluster)
library(network)
library(intergraph)
library(dplyr)
library(stargazer)
library(dils)
library(RColorBrewer)
```

# Analysis
````{r}
data_edges <- as.data.frame(read.csv(file = "edge-list.csv", header = FALSE))
data_edges_raw <- as.data.frame(read.csv(file = "edge-list.csv", header = FALSE))
data_nodes <- as.data.frame(read.csv(file = "ordered.csv", header = TRUE))

## Converting the edgelist to fix the vertex attributes
data_edges <- as.matrix(get.adjacency(graph.data.frame(data_edges)))
data_edges_graph <- graph.adjacency(data_edges)
# data_edges_graph <- as.undirected(data_edges_graph)

## Adding vertex attributes
data_edges_graph <- set.vertex.attribute(data_edges_graph,"dem", value = data_nodes$dem)
data_edges_graph <- set.vertex.attribute(data_edges_graph,"gni", value = data_nodes$gni)
data_edges_graph <- set.vertex.attribute(data_edges_graph,"geo", value = data_nodes$geo)

V(data_edges_graph)
vertex.attributes(data_edges_graph)
attributes(data_edges_graph)

## Make lists
countries <- V(data_edges_graph)$name
gni <- V(data_edges_graph)$gni
dem <- V(data_edges_graph)$dem
geo <- V(data_edges_graph)$geo

## Graphs

par(mfrow=c(2,2))

plot(data_edges_graph, #gni
     vertex.color = data_nodes$gni,
     vertex.size = data_nodes$gni/3500,
     edge.arrow.size = 0.1,
     #vertex.label = "",
     main = "Basic")

plot(data_edges_graph, #geo
     vertex.color = data_nodes$geo,
     vertex.size = igraph::degree(data_edges_graph),
     edge.arrow.size = 0.1,
     #vertex.label = "",
     main = "Geography")

plot(data_edges_graph, # dem
     vertex.color = data_nodes$dem,
     vertex.size = data_nodes$dem*2,
     edge.arrow.size = 0.1,
     #vertex.label = "",
     main = "Democracy Index")

# Final plots
plot(data_edges_graph, #basic
     vertex.color = data_nodes$geo,
     vertex.size = 6,
     edge.arrow.size = 0.1,
     #vertex.label = "",
     main = "Basic")

plot(data_edges_graph, #combined (gni)
     vertex.color = data_nodes$geo,
     vertex.size = data_nodes$gni/3500,
     edge.arrow.size = 0.1,
     vertex.label = "",
     main = "Gross National Income")

plot(data_edges_graph, #combined (dem)
     vertex.color = data_nodes$geo,
     vertex.size = data_nodes$dem*1.3,
     edge.arrow.size = 0.1,
     vertex.label = "",
     main = "Democracy Index")

plot(data_edges_graph, #combined (degree)
     vertex.color = data_nodes$geo,
     vertex.size = igraph::degree(data_edges_graph),
     edge.arrow.size = 0.1,
     vertex.label = "",
     main = "Degree Centrality")

plot(data_edges_graph, # indegree
     vertex.color = data_nodes$geo,
     vertex.size = igraph::degree(data_edges_graph, mode="in")*1.5,
     edge.arrow.size = 0.1,
     vertex.label = "",
     main = "In-Degree")

plot(data_edges_graph, # outdegree
     vertex.color = data_nodes$geo,
     vertex.size = igraph::degree(data_edges_graph, mode="out")*1.5,
     edge.arrow.size = 0.1,
     vertex.label = "",
     #layout = layout.fruchterman.reingold,
     main = "Out-Degree")

## Centralization
centr_degree(data_edges_graph)$centralization # 0.1733663
centr_betw(data_edges_graph)$centralization # 0.3295017
centr_clo(data_edges_graph)$centralization # closeness not well-defined for disconnected graphs, 0.06517578
centr_eigen(data_edges_graph)$centralization # 0.8779743

igraph::degree(data_edges_graph)
igraph::degree(data_edges_graph, mode="in")
igraph::degree(data_edges_graph, mode="out")
igraph::evcent(data_edges_graph)$vector 

edge_density(data_edges_graph) # 0.01575758
reciprocity(data_edges_graph) # 0.05128205
transitivity(data_edges_graph) # 0.05401662
````

## Testing ERGMs
````{r}
######### Converting to network object + displaying the network object
data_network <- asNetwork(data_edges_graph)
summary(data_network)

plot(data_network)

help('ergm-terms') # HELP ERGM TERMS :)

# DENSITY (edges) - WORKED
net.ergm <- ergm(data_network ~ edges)
summary(net.ergm) # Co-efficient for edges: -4.18802 
exp(net.ergm$coef) / (1 + exp(net.ergm$coef)) # Probability of tie forming: 0.01494949 
# The above is the density of the network... it's really not very dense.
gden(data_network) # 0.01575758 
#Note: every tie has about a 15% chance of being present... (double check this!)
mcmc.diagnostics(net.ergm)
net.ergm.gof <- gof(net.ergm)
plot(net.ergm.gof)

## RECIPROCITY (mutual)
summary(data_network ~ edges + mutual) # 148 edges, 4 mutual
net.ergm.rec <- ergm(data_network ~ edges + mutual, verbose=T)
mcmc.diagnostics(net.ergm.rec)
summary(net.ergm.rec)
net.ergm.rec.gof <- gof(net.ergm.rec)
plot(net.ergm.rec.gof)

## CLUSTERING (gwesp) - DID NOT WORK
summary(data_network ~ edges + gwesp)
net.ergm.gwe <- ergm(data_network ~ edges + gwesp, verbose=T)
summary()

## PREFERENTIAL ATTACHMENT (gwidegree and gwodegree)
summary(data_network ~ edges + gwidegree + gwodegree, verbose=T)
net.ergm.pref.gwi <- ergm(data_network ~ edges + gwidegree + gwodegree)
summary(data_network ~ edges + gwodegree, verbose=T)

## Transitivy - DID NOT WORK
summary(data_network ~ edges + transitive, verbose=T)
net.ergm.tran <- ergm(data_network ~ edges + transitive, verbose=T)
summary(net.ergm.tran)

## TRIANGLES - DID NOT WORK 
summary(data_network ~ edges + triangle) # 148 edges, 18 triangles
net.ergm.tri <- ergm(data_network ~ edges + triangle, verbose=T)
summary(net.ergm.tri)

## DEGREES - 
summary(data_network ~ degree)
````

# Actor-Attribute (dyadic-independent)
````{r}
##### GNI
net.gni <- data_network %v% 'gni' # the %v% extracts vertex  
summary(net.gni)
# Min: 380, Max: 83580, Mean: 16815
plot(data_network, vertex.cex=net.gni/15000) # PLOT GNI
plot(net.gni)
table(data_network %v% 'gni') 

## Model GNI
net.ergm.gni <- ergm(data_network ~ edges + nodecov('gni')) 
summary(data_network ~ edges + nodecov('gni')) # SUMMARY OF GNI MODEL
summary(net.ergm.gni)  

exp(net.ergm.gni$coef) / (1 + exp(net.ergm.gni$coef)) 
exp(net.ergm.gni$coef)
# edges: 0.01629778 -> 
# nodal cov gni: 0.4999993 -> 

net.ergm.gni.in <- ergm(data_network ~ edges + nodeicov("gni")) #in fact
summary(net.ergm.gni.in) 
exp(net.ergm.gni.in$coef) / (1 + exp(net.ergm.gni.in$coef)) 
# edges: 0.01432278
# in-degree edges: 0.5000063

net.ergm.gni.out <- ergm(data_network ~ edges + nodeocov("gni"))
summary(net.ergm.gni.out)
exp(net.ergm.gni.out$coef) / (1 + exp(net.ergm.gni.out$coef)) 
# edges: 0.01704071
# out-degree edges: 0.499780

##### Governance: Democracy index
net.dem <- data_network %v% 'dem' # the %v% extracts vertex  
plot(net.dem)
table(data_network %v% 'dem') 

## Model Dem index
summary(data_network ~ edges + nodecov('dem')) # SUMMARY OF DEM MODEL

plot(data_network, vertex.cex=net.dem/4, displaylabels=F) #GRAPH DEM
net.ergm.dem <- ergm(data_network ~ edges + nodecov('dem'))  
summary(net.ergm.dem)  
exp(net.ergm.dem$coef) / (1 + exp(net.ergm.dem$coef)) 
# edges: 0.01184656
# dem: 0.50495850

net.ergm.dem.in <- ergm(data_network ~ edges + nodeicov("dem")) #in fact
summary(net.ergm.dem.in) 
exp(net.ergm.dem.in$coef) / (1 + exp(net.ergm.dem.in$coef)) 
# edges: 0.01256766
# in-degree edges: 0.50736718

net.ergm.dem.out <- ergm(data_network ~ edges + nodeocov("dem"))
summary(net.ergm.dem.out)
exp(net.ergm.dem.out$coef) / (1 + exp(net.ergm.dem.out$coef)) 
# edges: 0.01410684
# out-degree edges: 0.50248749

## Geographical: Continent
net.geo <- data_network %v% 'geo' # the %v% extracts vertex  
plot(data_network, vertex.cex=net.geo, displaylabels=F) #GRAPH DEM
net.ergm.geo <- ergm(data_network ~ edges + nodefactor('geo'))  
summary(net.ergm.geo)  

# Model Geo
table(data_network %v% 'geo') 
exp(net.ergm.geo$coef) / (1 + exp(net.ergm.geo$coef)) 


net.ergm.geo.in <- ergm(data_network ~ edges + nodeifactor("geo")) #in fact
summary(net.ergm.geo.in) 
# edges: 0.01256766
# in-degree edges: 0.50736718

net.ergm.geo.out <- ergm(data_network ~ edges + nodeofactor("geo"))
summary(net.ergm.geo.out)
exp(net.ergm.geo.out$coef) / (1 + exp(net.ergm.geo.out$coef)) 
# edges: 0.01410684
# out-degree edges: 0.50248749
````

# Convergence
````{r}
# 
summary(data_network ~ edges + degree(1))
net.ergm.fit <- ergm(data_network ~ edges + degree(1))
mcmc.diagnostics(net.ergm.fit)

# 
````

````{r}
#### GOODNESS-OF-FIT (GOF)
model.01 <- ergm(data_network ~ edges + nodecov('gni') + nodecov('dem'))
summary(model.01) #gni if *

model.02 <- ergm(data_network ~ edges + nodeicov('gni') + nodeicov('dem'))
summary(model.02) # neither sig

model.03 <- ergm(data_network ~ edges + nodeocov('gni') + nodeicov('dem'))
summary(model.03) # GNI is sig***, Dem is * (cen) (closere)
mcmc.diagnostics(model.03)

model.04 <- ergm(data_network ~ edges + nodeicov('gni') + nodeocov('dem'))
summary(model.04) # Gni is ., dem is sig*** (clustered around few key nodes)

#### DEGENERACY
edges, cyclicalties, gwidegree, gwodegree, gwesp, gwdsp
````

# Combined model
````{r}
# edges
# 1: AG
# 2: APG
# 3: EE
# 4: GRULAC
# 5: WEOG

final.01 <- ergm(data_network ~ 
                   edges
                 + mutual
                 + nodeicov('gni')
                 + nodeocov('gni')
                 + absdiff('gni')
                 + nodeicov('dem')
                 + nodeocov('dem')
                 + absdiff('dem')
                 + nodefactor("geo"),
                 verbose=T)
summary(final.01)

exp(final.01$coef) / (1 + exp(final.01$coef)) 

final.01.dig <- mcmc.diagnostics(final.01)
final.01.gof <- gof(final.01)

plot(final.01.gof)

final.02 <- ergm(data_network ~ edges 
                 + mutual
                 + absdiff('gni')
                 + absdiff('dem')
                 + absdiff("geo"),
                 verbose=T)
summary(final.02)
final.02.dig <- mcmc.diagnostics(final.02)

## Goodness-of-fit
net.ergm.gof <- gof(model.05,  GOF = ~ idegree + odegree + espartners - model)
plot(net.ergm.gof)

````

# Things to check for
````{r}
- Model Degeneracy
- Convergence
````

# Other Important Data
*Recommendors GNI*
average	$23,758.11
53/54
Missing: The Holy See

*Receivers GNI*
average	$13,544.30
114/115
Missing: DPR Korea

*Recommendors Democracy Index*
average	6.345294118
51/54
Missing: Holy See, Liechtenstein, maldives

*Receivers Democracy Index*
average	5.376697248
109/115
Missing: Samoa, Somalia, South Sudan, Nauru, Kiribati, Nauru, Brunei

## Sources

The Economist Intelligence Unit: https://www.eiu.com/
Universal Periodic Review Database: https://www.upr-info.org/
World Bank: https://data.worldbank.org/

Rights/Laws: https://graphcommons.com/graphs/3dcbbda0-1843-4d24-b891-c5be13dd935c?show=analysis-cluster
